From physical principles to relativistic classical Hamiltonian and Lagrangian particle mechanics

### 2015-03-12 2014CompleteClassicalMechanics/completeClassicalMechanics.tex
Removed duplicated paragraph

\begin{defn}\label{inertialMass}
Let $dp_\alpha$ an infinitesimal interval of conjugate momentum and $du_\alpha\equiv d(g_{\alpha \beta}u^\beta)$ an infinitesimal interval of the covariant components of the four velocity. The ratio $m=n(dp_\alpha)/n(du_\alpha)$ between their relative label cardinality is called \emph{inertial mass}.
\end{defn}

\begin{defn}\label{invariantSpeed}
Let $p_\alpha$ be a component of conjugate momentum and $u_\alpha \equiv g_{\alpha \beta}u^\beta$ be a contravariant component of the four velocity. We define the \emph{inertial mass} as the cardinality conversion constant $m \equiv \mathfrak{C}^p_u$ between $p$ and $tu$. That is, if $dp=mdu$ then $n^p(dp)=n^u(du)$.
\end{defn}

>>>>

\begin{defn}\label{inertialMass}
Let $p_\alpha$ be a component of conjugate momentum and $u_\alpha \equiv g_{\alpha \beta}u^\beta$ be a contravariant component of the four velocity. We define the \emph{inertial mass} as the cardinality conversion constant $m \equiv \mathfrak{C}^p_u$ between $p$ and $u$. That is, if $dp_\alpha=mdu_\alpha$ then $n^p(dp_\alpha)=n^u(du_\alpha)$.
\end{defn}
